Titan GPU model

### 2020-06-04 code/TitanGPUmodel.Rmd
reproducibility

---
title: "Titan GPU model"
author: "GO"
output:
  html_document:
    css: style.css
    theme: cerulean
---
```{r setup, include=FALSE}
options(repos = c(CRAN = "http://cran.rstudio.com")) # set CRAN mirror
installed = installed.packages()
if(! "remotes" %in% installed) install.packages("remotes")
if(! ("forestmodel" %in% installed && packageVersion("forestmodel") >= "0.6.1"))
  remotes::install_github("NikNakk/forestmodel") # only package from GitHub
## all other packages will prompt to install from CRAN

out_dir = "../figs/" # paper related figures will go here
in_dir = "../data/" # input files live here
history_file = paste0(in_dir, "titan.gpu.history.txt")
service_nodes = paste0(in_dir, "titan.service.txt")
source("TitanGPUsetup.R")
Rmd.time = proc.time()
```
`r today()`
Read the data. Last inventory was run 01/20/2020 but Titan was turned off on 08/01/2019
```{r}
g_raw = fread(history_file, col.names = c("SN", "location", "insert", "remove"))
g_raw$remove[stringr::str_starts(g_raw$remove, "01/20/2020")] =
  "08/01/2019 20:07:33"
cat("Total of", (unique_SN = length(unique(g_raw$SN))), "unique SN\n")
cat("Total of", (unique_loc = length(unique(g_raw$location))),
    "unique locations\n")
```

@@

**Plot a sample** of `r nsample` locations ...
```{r}
loc_sample = sample(unique(gc_ev_nzg$location), nsample)
ev_sample = gc_ev_nzg %>% filter(location %in% loc_sample)
life_sample = gc_life %>% filter(location %in% loc_sample) %>% 
  separate(location, c(NA, "col", "row", "cage", "slot", "node"),
           sep = "[-csn]", convert = TRUE, remove = FALSE) %>%
  mutate(location = reorder(location, col)) # orders in increasing col
plot.life_ev(life_sample, ev_sample, location, "sample_loc", overlaps = FALSE)
```

@@

```{r}
gc_life = gc_life %>% select(SN, location, insert, remove, duration, out) %>%
  arrange(SN, remove, location)
gc_fulljoin = gc_life %>% full_join(gc_ev_fail, by = c("SN", "remove", "location"))
gc_full = gc_fulljoin %>% group_by(SN, remove, location) %>%
  mutate(insert = if_else(row_number() > 1, as.POSIXct(NA), insert),
         duration = if_else(row_number() > 1, as.numeric(NA), as.numeric(duration)),
         out = if_else(row_number() > 1, as.logical(NA), out)) %>% ungroup()
```
**Output** gc_full data frame to a CSV file for TBF analysis with Python code
```{r}
gc_write = as.data.frame(lapply(gc_full, as.character), stringsAsFactors = FALSE)
write_csv(gc_write, paste0(out_dir, "gc_full.csv"), na = "", col_names = TRUE)
```
**Message to reader of file:** All fields are character strings. Dates are with timezone. Missing values as "<NA>" strings.

@@

**Separate max_loc** into components (col, row, cage, slot, node). Note that this is the place this *SN* was located the longest. This muddies the hazard analysis somewhat as several locations can be the "treatment" for a given *SN*. But the proportions of time at max_loc tend to be very high. Time-dependent covariates, see: https://cran.r-project.org/web/packages/survival/vignettes/timedep.pdf
```{r}
gc_summary_loc = gc_summary %>% separate(max_loc, c(NA, "col", "row", "cage", "slot", "node"),
           sep = "[-csn]", convert = TRUE, remove = TRUE) %>% # c{col}-{row}c{cage}s{slot}n{node}
  mutate( col = as.factor(col), row = as.factor(row), cage = as.factor(cage), 
          slot = as.factor(slot), node = as.factor(node),
          days = time/(60*60*24),
          years = days/365,
          dead = out & dbe + otb > 0,
          dead_otb = out & otb > 0,
          dead_dbe = out & dbe > 0) # define fail & censored

gc_summary_loc_o = gc_summary_loc %>% filter(batch == "old")
gc_summary_loc_n = gc_summary_loc %>% filter(batch == "new")
gc_summary_loc_censor1 = gc_summary_loc %>% 
  mutate(dead = if_else(batch == "old" & years > 1, FALSE, dead), 
         days = if_else(batch == "old" & years > 1, 1*365, days),
         years = if_else(batch =="old" & years > 1, 1, years))  # censor at 1 year
gc_summary_loc_censor2 = gc_summary_loc %>% 
  mutate(dead = if_else(batch == "old" & years > 2, FALSE, dead), 
         days = if_else(batch == "old" & years > 2, 2*365, days),
         years = if_else(batch =="old" & years > 2, 2, years))  # censor at 2 years
gc_summary_loc_censor3 = gc_summary_loc %>% 
  mutate(dead = if_else(batch == "old" & years > 3, FALSE, dead), 
         days = if_else(batch == "old" & years > 3, 3*365, days),
         years = if_else(batch =="old" & years > 3, 3, years))  # censor at 3 years
gc_summary_loc_censor4 = gc_summary_loc %>% 
  mutate(dead = if_else(batch == "old" & years > 4, FALSE, dead), 
         days = if_else(batch == "old" & years > 4, 4*365, days),
         years = if_else(batch =="old" & years > 4, 4, years))  # censor at 4 years
```
**Output** gc_full to a CSV file
```{r}
gc_write = as.data.frame(lapply(gc_summary_loc, as.character), stringsAsFactors = FALSE)
write_csv(gc_write, paste0(out_dir, "gc_summary_loc.csv"), na = "", col_names = TRUE)
```
Get some stats for sanity check.
```{r}
cat("Total", nrow(gc_summary_loc), "unique lifetimes\n")
cat("  Censored:", sum(!gc_summary_loc$dead), "  dead:", sum(gc_summary_loc$dead),
    "  Known alive:", sum(!gc_summary_loc$out), "\n")
cat("  DBE or OTB during life:", sum(gc_summary_loc$dbe > 0 | gc_summary_loc$otb >0), "\n")
cat("           More than one:", sum(gc_summary_loc$dbe + gc_summary_loc$otb > 1, na.rm = TRUE), "\n")
ggplot(gc_summary_loc, aes(x = time)) + geom_histogram(bins = 60) + ggtitle("GPU Life Times")
ggplot(gc_summary_loc, aes(x = time)) + geom_histogram(bins = 60) + 
  facet_wrap(~ batch) + ggtitle(paste("GPU Life Times - new and old"))
ggplot(gc_summary_loc, aes(x = time_max_loc)) + geom_histogram(bins = 200) +
  ggtitle("Life Proportion at Longest Location") + theme_bw()
ggplot((gc_summary_loc %>% filter(dead)), aes(x = time_max_loc)) +
      geom_histogram(bins = 200) + theme_bw() +
      ggtitle("Life Proportion at Longest Location - Dead Only")
```

>>>>

---
title: "Titan GPU model"
author: "GO"
output:
  html_document:
    css: style.css
    theme: cerulean
---
```{r setup, include=FALSE}
options(repos = c(CRAN = "http://cran.rstudio.com")) # set CRAN mirror
installed = installed.packages()
if(! "remotes" %in% installed) install.packages("remotes")
if(! ("forestmodel" %in% installed && packageVersion("forestmodel") >= "0.6.1"))
  remotes::install_github("NikNakk/forestmodel") # only package from GitHub
## all other packages will prompt to install from CRAN
library(data.table)
library(magrittr)
library(dplyr)
library(ggplot2)
library(forcats)
library(lubridate)
library(survival)
library(survminer)
library(forestmodel)

out_dir = "../figs/" # paper related figures will go here
in_dir = "../data/" # input files live here
history_file = paste0(in_dir, "titan.gpu.history.txt")
service_nodes = paste0(in_dir, "titan.service.txt")
source("TitanGPUsetup.R")
Rmd.time = proc.time()
```
`r`
Read the data. Last inventory was run 01/20/2020 but Titan was turned off on 08/01/2019
```{r}
g_raw = fread(history_file, col.names = c("SN", "location", "insert", "remove"))
g_raw$remove[stringr::str_starts(g_raw$remove, "01/20/2020")] =
  "08/01/2019 20:07:33"
cat("Total of", (unique_SN = length(unique(g_raw$SN))), "unique SN\n")
cat("Total of", (unique_loc = length(unique(g_raw$location))),
    "unique locations\n")
```

@@

**Plot a sample** of `r nsample` locations ...
```{r}
loc_sample = sample(unique(gc_ev_nzg$location), nsample)
ev_sample = gc_ev_nzg %>% filter(location %in% loc_sample)
life_sample = gc_life %>% filter(location %in% loc_sample) %>% 
  tidyr::separate(location, c(NA, "col", "row", "cage", "slot", "node"),
           sep = "[-csn]", convert = TRUE, remove = FALSE) %>%
  mutate(location = reorder(location, col)) # orders in increasing col
plot.life_ev(life_sample, ev_sample, location, "sample_loc", overlaps = FALSE)
```

@@

```{r}
gc_life = gc_life %>% select(SN, location, insert, remove, duration, out) %>%
  arrange(SN, remove, location)
gc_fulljoin = gc_life %>% full_join(gc_ev_fail, by = c("SN", "remove", "location"))
gc_full = gc_fulljoin %>% group_by(SN, remove, location) %>%
  mutate(insert = if_else(row_number() > 1, as.POSIXct(NA), insert),
         duration = if_else(row_number() > 1, as.numeric(NA), as.numeric(duration)),
         out = if_else(row_number() > 1, as.logical(NA), out)) %>% ungroup()
```
**Output** gc_full data frame to a CSV file for TBF analysis with Python code
```{r}
gc_write = as.data.frame(lapply(gc_full, as.character), stringsAsFactors = FALSE)
readr::write_csv(gc_write, paste0(out_dir, "gc_full.csv"), na = "", col_names = TRUE)
```
**Message to reader of file:** All fields are character strings. Dates are with timezone. Missing values as "<NA>" strings.

@@

**Separate max_loc** into components (col, row, cage, slot, node). Note that this is the place this *SN* was located the longest. This muddies the hazard analysis somewhat as several locations can be the "treatment" for a given *SN*. But the proportions of time at max_loc tend to be very high. Time-dependent covariates, see: https://cran.r-project.org/web/packages/survival/vignettes/timedep.pdf
```{r}
gc_summary_loc = gc_summary %>% tidyr::separate(max_loc, c(NA, "col", "row", "cage", "slot", "node"),
           sep = "[-csn]", convert = TRUE, remove = TRUE) %>% # c{col}-{row}c{cage}s{slot}n{node}
  mutate( col = as.factor(col), row = as.factor(row), cage = as.factor(cage), 
          slot = as.factor(slot), node = as.factor(node),
          days = time/(60*60*24),
          years = days/365,
          dead = out & dbe + otb > 0,
          dead_otb = out & otb > 0,
          dead_dbe = out & dbe > 0) # define fail & censored

gc_summary_loc_o = gc_summary_loc %>% filter(batch == "old")
gc_summary_loc_n = gc_summary_loc %>% filter(batch == "new")
gc_summary_loc_censor1 = gc_summary_loc %>% 
  mutate(dead = if_else(batch == "old" & years > 1, FALSE, dead), 
         days = if_else(batch == "old" & years > 1, 1*365, days),
         years = if_else(batch =="old" & years > 1, 1, years))  # censor at 1 year
gc_summary_loc_censor2 = gc_summary_loc %>% 
  mutate(dead = if_else(batch == "old" & years > 2, FALSE, dead), 
         days = if_else(batch == "old" & years > 2, 2*365, days),
         years = if_else(batch =="old" & years > 2, 2, years))  # censor at 2 years
gc_summary_loc_censor3 = gc_summary_loc %>% 
  mutate(dead = if_else(batch == "old" & years > 3, FALSE, dead), 
         days = if_else(batch == "old" & years > 3, 3*365, days),
         years = if_else(batch =="old" & years > 3, 3, years))  # censor at 3 years
gc_summary_loc_censor4 = gc_summary_loc %>% 
  mutate(dead = if_else(batch == "old" & years > 4, FALSE, dead), 
         days = if_else(batch == "old" & years > 4, 4*365, days),
         years = if_else(batch =="old" & years > 4, 4, years))  # censor at 4 years
```
**Output** gc_full to a CSV file
```{r}
gc_write = as.data.frame(lapply(gc_summary_loc, as.character), stringsAsFactors = FALSE)
readr::write_csv(gc_write, paste0(out_dir, "gc_summary_loc.csv"), na = "", col_names = TRUE)
```
Get some stats for sanity check.
```{r}
cat("Total", nrow(gc_summary_loc), "unique lifetimes\n")
cat("  Censored:", sum(!gc_summary_loc$dead), "  dead:", sum(gc_summary_loc$dead),
    "  Known alive:", sum(!gc_summary_loc$out), "\n")
cat("  DBE or OTB during life:", sum(gc_summary_loc$dbe > 0 | gc_summary_loc$otb >0), "\n")
cat("           More than one:", sum(gc_summary_loc$dbe + gc_summary_loc$otb > 1, na.rm = TRUE), "\n")
ggplot(gc_summary_loc, aes(x = time)) + geom_histogram(bins = 60) + ggtitle("GPU Life Times")
ggplot(gc_summary_loc, aes(x = time)) + geom_histogram(bins = 60) + 
  facet_wrap(~ batch) + ggtitle(paste("GPU Life Times - new and old"))
ggplot(gc_summary_loc, aes(x = time_max_loc)) + geom_histogram(bins = 200) +
  ggtitle("Life Proportion at Longest Location") + theme_bw()
ggplot((gc_summary_loc %>% filter(dead)), aes(x = time_max_loc)) +
      geom_histogram(bins = 200) + theme_bw() +
      ggtitle("Life Proportion at Longest Location - Dead Only")
```
